\documentclass[a4paper]{article} %
\usepackage{graphicx,amssymb} %
\usepackage{setspace}
\usepackage{indentfirst}

\textwidth=15cm \hoffset=-1.2cm %
\textheight=25cm \voffset=-2cm %

\pagestyle{empty} %

\date{} %

\def\keywords#1{\begin{center}{\bf Keywords}\\{#1}\end{center}} %

\def\titulo#1{\title{#1}} %
\def\autores#1{\author{#1}} %

% Please, do not change any of the above lines

\begin{document}

% Type down your paper title
\titulo{ChalkBoard: The Story of Font Packs}

% Authors
\autores{Justin Brown, Dzu Pham, Jacob Drilling, Billy Rhoades, Sam Pilla \\ %
       Missouri University of Science and Technology \\
       }%
\doublespace

\maketitle

\thispagestyle{empty}



% The abstract

\begin{abstract}

This report contains the methods and models of execution for developing the Android application ChalkBoard. Using SCRUM we developed the software over the course of 3.5 weeks. We began by designing an outline for the application, one that would keep track of assignments for classes and their grades. We created a GitHub repository so that outside of SCRUM meetings we could monitor progress and be able to revert to working changes if a step in the development of the software was broken.

(Insert other things here)

\end{abstract}

\section*{Introduction}

College students are always on the move, whether it be from home to school, activity to project, or homework to sleep. They need something to keep track of their academics, so we created that tool for them.

ChalkBoard is a tool that keeps track of your class and grade needs. It will handle the math for you, calculating your current grade with categories, each able to be weighted differently so each class is represented appropriately.

(Probably also needs more stuff and fine tuning)

\section*{Body of Report}

Insert Body of Report here.

\section*{Conclusion}

Insert Conclusion here.

\section*{References}

Insert References here.

\section*{Appendix}

Source Code: https://github.com/ArthurSemilla/cs3100

\end{document}
